\TheTitle

### 2015-08-17 linvis.tex
Editing: Implementation details

\section{Implementation Details}
We built a we-based tool to provide information about the kernel.
We chose to use Nginx as the main web server, postgresql as the dbms, and Flask
as the framework for generating the dynamic content.

Nginx is a high-performance, scalable HTTP and mail server. Started in 2002,
the project is much younger than the Apache project, and designed with massive
scalability and multi-processing in mind. Instead of using request-driven
threading, Nginx uses an event-driven architecture, making it more scalable,
proving itself as being the web server behind Netflix, Hulu, GitHub, Tumblr,
and many other popular sites.

Postgresql is our dbms of choice, providing fast and reliable results. There
are multiple reasons behind choosing postgresql over another dbms. The main
reason being that the dataset provided from \evantodo{paper} was generated from
a postgresql database, allowing us to import the data directly without any
further conversions. The secondary reason is that we are more familiar with
postgresql than the other systems available.

We chose the python micro-framework Flask for generating the dynamic content.
Working with flask is simple and easy.

@@

\evantodo{Talk a bit about the heuristics used for building the tree from the
DAG}

@@

\subsection{Performance}
The modules and list tree view still use the old method of gathering the
information for the respective view type. For single commits or very small
merges, getting everything directly from the database and generating the pages
server-side performs better than using the asynchronous requests, there
isn't the overhead of multiple round trips. As the size of the merges grow,
the performance becomes far worse than the asynchronous system and in some
cases will time out. The asynchronous approach adds some overhead, profiled at
roughly 500ms, regardless of the response size. The asynchronous approach has
many benefits over building the response on the server, including spinners, a
public API, and lower response times for larger merges. Further work can be
done to improve the results beyond the response time of 500ms using improved
queries and more efficient methods of building the tree. \newpage

>>>>

\section{Implementation Details}
We built a web-based tool to provide information about the kernel.
We chose to use Nginx as the main web server, postgresql as the dbms, and Flask
as the framework for generating the dynamic content.

Nginx is a high-performance, scalable HTTP and mail server. Started in 2002,
the project is much younger than the Apache project, and designed with massive
scalability and multi-processing in mind. Instead of using request-driven
threading, Nginx uses an event-driven architecture, making it more scalable,
proving itself as being the web server behind large sites like Netflix, Hulu,
GitHub, Tumblr, and many other popular
sites\footnote{\url{http://wiki.nginx.org/Main}}.

Postgresql is our dbms of choice, providing fast and reliable results. There
are multiple reasons behind choosing postgresql over another dbms. The main
reason being that the dataset built by German et al. was generated from
a postgresql database, allowing us to import the data directly without any
further conversions. The secondary reason is that we are more familiar with
postgresql than the other systems available.

We chose the python micro-framework
Flask\footnote{\url{http://flask.pocoo.org/docs/0.10/}} for generating the
dynamic content.  Working with flask is simple and easy, allowing us to work in
Python.

@@

@@

\subsection{Performance}
The modules and list tree view still use the old method of gathering the
information for the respective view type. For single commits or very small
merges, getting everything directly from the database and generating the pages
server-side performs better than using the asynchronous requests, there
isn't the overhead of multiple round trips. As the size of the merges grow,
the performance becomes far worse than the asynchronous system and in some
cases will time out. The asynchronous approach adds some overhead, profiled at
roughly 500ms, regardless of the response size. The asynchronous approach has
many benefits over building the response on the server, including spinners, a
public API, and lower response times for larger merges. Further work can be
done to improve the results beyond the response time of 500ms using improved
queries and more efficient methods of building the tree.
